---
title: "Untitled"
author: "Matthew Wigginton Conway"
date: "8/22/2014"
output: html_document
---

```{r}
source('~/memphis/scripts/analysis/domatching.R')
```
       
We run a bunch of matching to try to determine if rehabilitating a house has a significant impact on the 
values of the homes around it.

First we set some general parameters, namely how many trees to use in random forest proximity matching and what our covariates are.

```{r}
trees <- 25000
covariates <- c('logrtotapr', 'age', 'rmbed', 'fixbath', 'sqft','count_minor_250', 'count_severe_250',  'count_minor_500', 'count_severe_500', 'blight', 'medianhhinc', 'pctunemployed', 'pctownocc')
```
# Non-demolition investment
Does putting a significant investment into a property raise the values of the the properties around it? We match sales around
blighted homes which received investment between 2008 and 2010 with similar sales within 2 miles, but which are not near blighted homes.

## Post-rehab evaluation

We look to see if there is a treatment effect post-rehab.

### Spatial matching

Match only to homes within 2 miles. We use both propensity and proximity matching.

```{r  rehabpostSpat, dev='png'}
# propensity score matching
m <- doMatching(covariates, method='prop', trees=trees)
bal(m[[1]], m[[2]], covariates)
summary(m[[1]])

# proximity score matching (Savage et al forthcoming)
m <- doMatching(covariates, trees=trees)
bal(m[[1]], m[[2]], covariates)
summary(m[[1]])

df <- data.frame(treatment=m[[2]][m[[1]]$index.treated,'parid'], control=m[[2]][m[[1]]$index.control,'parid'])
write.csv(df, 'spatial.csv', row.names=F)
```

### Aspatial matching

Match to homes anywhere in the city. The tradeoff between spatial and aspatial matching is that using aspatial matching
(which is the same as using an infinite radius and spatial matching) allows one to better match on the observed features,
at the expense of matching on unobserved features. It is assumed that unobserved features follow the First Law of Geography,
namely that things near each other tend to be similar, so by matching to nearby houses unobserved features should
be similar.

```{r  rehabpostAspat, dev='png'}
# propensity score matching
m <- doMatching(covariates, method='prop', matches=NULL, trees=trees)
bal(m[[1]], m[[2]], covariates)
summary(m[[1]])

# proximity score matching
m <- doMatching(covariates, matches=NULL, trees=trees)
bal(m[[1]], m[[2]], covariates)
summary(m[[1]])

df <- data.frame(treatment=m[[2]][m[[1]]$index.treated,'parid'], control=m[[2]][m[[1]]$index.control,'parid'])
write.csv(df, 'aspatial.csv', row.names=F)
```