---
title: "Untitled"
author: "Matthew Wigginton Conway"
date: "8/22/2014"
output: html_document
---

```{r}
source('~/memphis/scripts/analysis/domatching.R')
```
       
We run a bunch of matching to try to determine if rehabilitating a house has a significant impact on the 
values of the homes around it.

First we set some general parameters, namely how many trees to use in random forest proximity matching and what our covariates are.

```{r}
trees <- 25000
covariates <- c('logrtotapr', 'age', 'rmbed', 'fixbath', 'sqft','count_minor_250', 'count_severe_250',  'count_minor_500', 'count_severe_500', 'blight', 'medianhhinc', 'pctunemployed', 'pctownocc')
```


## Do the same thing before the rehabs occurred

This nonsensical situation would indicate that we messed up.

```{r rehabpre, dev='png'}
# spatial
# propensity score matching
m <- doMatching(covariates, method='prop', post=F, trees=trees)
bal(m[[1]], m[[2]], covariates)
summary(m[[1]])

# proximity score matching
m <- doMatching(covariates, post=F, trees=trees)
bal(m[[1]], m[[2]], covariates)
summary(m[[1]])

# aspatial
# propensity score matching
m <- doMatching(covariates, method='prop', post=F, matches=NULL, trees=trees)
bal(m[[1]], m[[2]], covariates)
summary(m[[1]])

# proximity score matching
m <- doMatching(covariates, post=F, matches=NULL, trees=trees)
bal(m[[1]], m[[2]], covariates)
summary(m[[1]])
```